\chapter{Project Plan}

The current plan for the project follows as below:

\subsection*{November 2022 - January 2023}
By the new year, the preliminary research will be completed to make way for the start of the Literature Review and the programming of the first language model.

\subsection*{January 2023 - April 2023}
By the start of April, the first two language models will be completed, tested and investigated. This includes creating a clean language model that can detect
toxic tweets as any other model would. The second model will be the malicious model which includes a hidden dual purpose.

Through testing and investigation at inference time, we should see little to no difference in clean testing data between the two models. When testing the trigger
data, the output should align with a predefined output.

\subsection*{April 2023 - May 2023}
Once the two models have been created, I will begin probing the models to look for differences between the two that would indicate that one has a hidden purpose. 
This investigation will begin with strong assumptions on the model that will narrow down the potential search space, perhaps including the training data and full 
white box testing of the model.

\subsection*{May 2023 - June 2023}
During May, we will begin to relax the assumptions to arrive at a set of weak assumptions that do not tell us much about the nature of the model. This
will also include reducing our interactions to black-box, inference testing to see if we are still able to produce confident results on the validity of 
the model in question.

\subsection*{June 2023}
The end of the project timeline will then be reserved for writing up the report and creating any statistics using the models required for the report to be completed by the 
19th of June 2023.
