\chapter{Ethical Issues}

\section{Harmful Use}

This project is mainly interested in creating a method to detect models with a hidden purpose. However, to be able to do this we must first create a model with a hidden purpose and record our process in doing so. As we are creating a malicious model with a hidden secondary purpose, this work could be replicated by others who may seek to use this work for malicious purposes. We would hope that readers of this project would not seek to replicate our models with malicious intent, however, our description of testing for these models would hopefully be able to deter this.

\section{Harmful Training Data}

Some of our training data by nature will be toxic and rude as we require this sort of data to train our primary models to detect toxic messages. This data may offend certain people due to its hateful nature. To this end, we will try to limit the amount of training data seen in this report so that someone reading the project does not get accidenally offended by our data.

\section{Environmental}

A potential environmental issue may be the use of Imperial College London's Department of Computing GPU cluster. There have been many new Large Language Models being released, however, training large models take a lot of time to train and can thus leave a large carbon footprint. We have seen this with ChatGPT (which uses the GPT-3 model), the carbon footprint for training the model was equivalent to releasing over 500 tons of CO2e \cite{chat_gpt_environment}. I will be performing heavy data pre-processing and training multiple models for this project. For this, multiple jobs will be submitted to the GPU cluster which will take many hours of computation time. Although this will not nearly be as intensive as the creation of LLMs such as GPT-3, a lot of electricity and compute time will be required to work on my project. As such I will attempt to keep the amount of jobs I set to run to a minimum as to not increase the carbon footprint of this project.

\section{Licensing}

We will also comply with any licensing that will arise from using training data, pre-trained models or language models to create data and ensure any data we do use has been obtained legally and ethically. Finally, we will ensure that any data used does not have personally identifying data attached.